%-------------------------
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}
% \setlength{\footskip}{5pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
    \textbf{\Huge \scshape Liheng Cao} \\ \vspace{1pt}
    \href{mailto:lihengcao@gmail.com}{\underline{Email}} $|$ 
    \href{https://linkedin.com/in/lihengcao}{\underline{LinkedIn}} $|$
    \href{https://github.com/lihengcao}{\underline{GitHub}} $|$
    \href{https://lihengcao.github.io}{\underline{More on my (lightweight) personal website}}
\end{center}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{New York University, Tandon School of Engineering}{Brooklyn, New York}{Bachelor of Science in Computer Science, Minor in Mathematics, Magna Cum Laude}{Sep. 2019 -- May 2022}
\resumeSubHeadingListEnd

% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Meta}{Aug. 2022 -- Feb, 2024}{Software Engineer on FB NewsFeed - Feed Health}{Seattle, WA}
        \resumeItemListStart
            \resumeItem{Working on making FB Main NewsFeed faster - both efficiency and latency - and more reliable.}
            \resumeItem{Designed, implemented, \& deployed automatic throttling platform across Feed to auto-mitigate an entire class of reliability regressions, preventing overnight pages for simple to fix issues.}
            \resumeItem{Saved \$2M from CPU and Database wins by identifying low hanging fruit and optimizing, experimenting, and reviewing.}
            \resumeItem{Augmented internal tools to increase developer velocity for identifying efficiency wins.}
            \resumeItem{As part of a tier 1 oncall, prevented major regressions from taking down the site and reducing user experience adn revenue.}
        \resumeItemListEnd

    \resumeSubheading{Machines in Motion Lab at NYU Tandon}{Jun. 2021 -- May 2022}{Undergraduate Research Assistant}{Brooklyn, NY}
        \resumeItemListStart
            \resumeItem{Researched contact detection for legged locomotion and path integral for policy improvement}
            \resumeItem{Assembled, tested, and repaired robots for research and class}
            \resumeItem{Created Python/C++ bindings for IMU sensor, and modified USB drive and serial reader code}
            \resumeItem{Created and merged many small pull requests to fix documentation and code}
            \resumeItem{Operated Vicon motion tracking system and integrated with robot motion}
            \resumeItem{Created poster documenting research}
        \resumeItemListEnd
      
    \resumeSubheading{NYU RoboSub VIP Team at NYU Tandon}{Aug. 2021 -- May 2022}{Software Team Lead}{Brooklyn, NY}
        \resumeItemListStart
            \resumeItem{Assigned tasks and supervised team members in motor control, vision, task planning, and localization}
            \resumeItem{Researched relevant topics and trained the team}
            \resumeItem{Developed the vision and task planning of the robot}
            \resumeItem{Will compete in the RoboSub competition}
        \resumeItemListEnd
      
    \resumeSubheading{NYU Robotic Design Team VIP Team at NYU Tandon}{Sep. 2020 -- Sep. 2021}{Software Competency Member}{Brooklyn, NY}
        \resumeItemListStart
            \resumeItem{Competed in the NASA Robotics Mining Competition}
            \resumeItem{Wrote code for communication between server and robot}
            \resumeItem{Integrated sensor data to control the robot}
        \resumeItemListEnd
    
\resumeSubHeadingListEnd

% PROJECTS
\section{Projects | more on \texorpdfstring{\href{https://github.com/lihengcao}{\underline{GitHub}}}{GitHub} and \texorpdfstring{\href{https://lihengcao.github.io}{\underline{Personal website}}}{Personal website}}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Cost Splitter App} $|$ \emph{HTML, JS}}{Jan. 2022}
        \resumeItemListStart
            \resumeItem{Built a Cost Splitter app from scratch using basic web dev. for my roommates}
            \resumeItem{Receives name, price, and people to split amongst}
            \resumeItem{Outputs how much each person pays}
            \resumeItem{Allows roommates to split group grocery runs at Costco}
        \resumeItemListEnd
        
    \resumeProjectHeading{\textbf{CRUD App} $|$ \emph{Go}}{Nov. 2021}
        \resumeItemListStart
            \resumeItem{Built a distributed Create, Read, Update, Delete database app using Go}
            \resumeItem{Split into multiple frontends and backends}
            \resumeItem{Implemented the Raft consensus algorithm}
            \resumeItem{App could be accessed from multiple frontends, and data was distributed over multiple backends}
        \resumeItemListEnd
        
    \resumeProjectHeading{\textbf{Sign Language Classifier} $|$ \emph{Python, Jupyter Suite}}{Apr. 2021}
        \resumeItemListStart
            \resumeItem{Trained various models with a partner to classify the MNIST Sign Language dataset}
            \resumeItem{Created a presentation of results and presented to members of the Introduction to Machine Learning course}
        \resumeItemListEnd
        
    \resumeProjectHeading{\textbf{SCUDEM V 2020 Differential Equations Modelling Competition} $|$ \emph{Processing, Java}}{Nov. 2020}
        \resumeItemListStart
            \resumeItem{Modeled and animated the physics of a bird spinning around on a bicycle wheel as a part of a 3 man team}
            \resumeItem{Scored the highest score (4.875/5) out of 180 other teams}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Other/SKILLS-----------
\section{}
\textbf{Relevant Competencies:} Software Engineering, Research, Robotics, Leadership, Machine Learning, and Computer Vision \\
\textbf{Relevant Coursework:} Numerical Computing, Theory of Computation, Data Science, Algorithmic Machine Learning, Parallel and Distributed Systems, Computer Graphics, Haptics and Telerobotics, Operating Systems, Computer Networking, Algorithms \\

\end{document}